\section{Gochujang Garlic Noodles}

\begin{itemize}
\item 4 green onions, thinly sliced (separate the white and green pieces)
\item 14-20 cloves of garlic, finely chopped
\item 4 baby bok choy, halved or quartered lengthwise
\item 1 lb ground beef (or pork, chicken, etc.)
\item 2 lbs frozen udon noodles
\item Sesame seeds (as garnish)
\item Soft-boiled eggs (optional, for serving)
\item 4 tbsp Korean chili pepper flakes (gochugaru)
\item 2 tbsp sugar
\item 2 tbsp soy sauce
\item 1 tbsp oyster sauce
\item 2 tbsp mirin
\item 2 tbsp Korean soybean paste (doenjang)
\item 4 tbsp Korean chili paste (gochujang)
\end{itemize}

\subsection{Note}

You’ll want to use a wok or a very large pan for this, since you’ll be putting all the noodles in there at some point.
Or you can half the recipe (I like to make enough for leftovers) so that a smaller pan could work.

Rather than blanching the bok choy in the pasta water, you could instead steam a little less than 2 crowns of broccoli
to go along with the noodles.

\begin{enumerate}
\item In a small container, mix the following together:
\begin{itemize}
    \item gochugaru
    \item sugar
    \item soy sauce
    \item oyster sauce
    \item mirin
    \item doenjang
    \item gochujang
\end{itemize}
\item In a wok, heat oil over medium-high heat. Once heated, add the ground beef, breaking it up and rendering out the
    fat for 2 minutes.
\item Add the garlic and white parts of the green onions, cooking for 2 minutes longer.
\item Reduce the heat to low, add the seasoning paste. Give it a good stir and cook for 2 more minutes.  Turn off the
    heat (if using broccoli, this is when you’ll want to start the steaming process).
\item Meanwhile, bring a pot of water to a boil. Cook the noodles a little less than the package instruc- tions. Take
    them out and rinse under cold water, reserving the water.
\item In the same water, blanch the bok choy for 1 minute. Drain and set aside.
\item Add 0.5 cup of the pasta water to the sauce and bring to a boil over high heat. Add the drained noodles to the wok
    and toss together for a minute until the noodles are completely coated.
\item Serve the noodles into bowls, garnishing with bok choy, green onions, sesame seeds, and soft-boiled eggs (if
    using).
\end{enumerate}
