\section{Marry Me Chicken}

\begin{itemize}
\item 3 tbsp all-purpose flour
\item 4 thin-sliced chicken breasts (about 1.25 lbs; see note)
\item 2 tablespoons extra-virgin olive oil
\item 1 small yellow onion, finely chopped
\item 3 cloves garlic, minced
\item 1 cup heavy cream
\item 1 cup chicken broth
\item 0.33 cup sun-dried tomatoes packed in oil, drained and finely chopped
\item 2 teaspoons tomato paste
\item 0.5 teaspoon dried oregano
\item 0.25 teaspoon crushed red pepper flakes
\item 0.25 teaspoon sugar
\item 2 tablespoons grated Parmigiano Reggiano or Pecorino Romano cheese
\item 2 tablespoons fresh chopped basil, plus more for serving
\end{itemize}

\begin{enumerate}
\item Place the following in a ziplock bag and shake to combine to coat the chicken evenly
\begin{itemize}
    \item flour
    \item salt
    \item black pepper
    \item chicken
\end{itemize}
\item In a large skillet over medium-high heat, cook the chicken for about 2 minutes on each side until it’s lightly
    golden and just cooked through. Transfer the chicken to a plate.
\item Reduce the heat to medium and add the onions. Cook, stirring frequently, until they are softened and translucent
    (2-3 minutes).
\item Add garlic and stir constantly for 30 seconds.
\item Add the following, and use a spoon to scrape the brown bits from the pan into the liquid.
\begin{itemize}
    \item cream
    \item broth
    \item sun-dried tomatoes
    \item tomato paste
    \item oregano
    \item red pepper flakes
    \item sugar
    \item salt
\end{itemize}
\item Bring to a boil, then reduce the heat to medium and gently boil, uncovered, until the sauce is thickened (about 5
    minutes).
\item Stir in the Parmigiano Reggiano and basil. Add the chicken back to the pan along with any juices.
\item Reduce the heat to low and simmer unitil the chicken is warmed through and the sauce thickens a bit more (1-2
    minutes).
\item Sprinkle with more fresh basil and serve.
\end{enumerate}

\subsection{Note}

You can use pre-cut, ready-to-cook, thin-sliced chicken breasts for this recipe. If you’d like to use regular chicken
breasts, you’ll need to first cut them in half horizontally to form flat fillets, then pound them until they are between
an eighth and quarter-inch thick. (It’s important to cut them in half first; otherwise they’ll be enormous after
pounding.)
