\section{Mushroom Ragu}

\begin{itemize}
\item 1 large yellow onion, chopped
\item 2 to 3 carrots, peeled and chopped
\item 4 to 5 garlic cloves, minced
\item 6 oz portabella mushrooms, chopped
\item 6 oz shiitake mushrooms, sliced
\item 8 oz baby bella mushrooms, sliced
\item 1 cup low-sodium vegetable broth
\item 0.5 tablespoon fresh thyme leaves
\item 1 teaspoon dried oregano
\item 0.5 cup chopped fresh parsley, more for later
\item 1 cup dry red wine (can just use more vegetable broth)
\item 15 oz can tomato sauce
\item 2 to 3 tablespoons chopped hazelnuts, optional
\end{itemize}

\begin{enumerate}
\item Cook the following in a large pot until the vegetables have softened, about 5 minutes.
\begin{itemize}
    \item onions
    \item carrots
    \item garlic
    \item salt
\end{itemize}
\item Add the following ingredients, cook for about 5 minutes until the mushrooms being to soften.
\begin{itemize}
    \item mushrooms
    \item drizzle of olive oil.
    \item a little bit of broth
    \item salt
\end{itemize}
\item Add these ingredients, then bring to a boil for 5 minutes.
\begin{itemize}
    \item thyme
    \item oregano
    \item parsley
    \item black pepper
    \item red wine
    \item tomato sauce
    \item remainder of vegetable broth
\end{itemize}
\item Reduce the heat to low and cover, cooking for 20 minutes or so.
\item Uncover and allow the mushrooms to cook some more (15-20 minutes) until the mixture thickens to a ragu.
\item Taste and adjust seasonings, stir in a bit of fresh parsley and optional chopped hazelnuts.
\item Serve with pasta, polenta, couscous, etc.
\end{enumerate}
