\section{Spaghetti Frittata}

\begin{itemize}
\item 6 oz package spinach
\item 8 oz baby bella mushrooms, thinly sliced
\item 5 eggs
\item 0.5 small package fresh basil, ribboned
\item 1 clove garlic, minced
\item 1.5 oz Parmesan cheese, finely grated
\item 4 slices prosciutto
\item 5 oz spaghetti
\item 1 yellow onion, medium diced
\item 0.5 tbsp Italian seasoning
\end{itemize}

\subsection{Note}

I suggest doing all the slicing and cheese shredding ahead of time, as this recipe will have you doing quite a few
things at the same time. The skillet you use also needs to be broiler-safe!

\begin{enumerate}
\item Combine the following in a bowl and set aside:
\begin{itemize}
    \item Onion
    \item Garlic
    \item Mushroom
    \item Italian seasoning
    \item Salt
    \item Pepper
\end{itemize}
\item Fill a medium saucepan with hot water and bring to a boil. Once boiling, add salt and pasta, cook until desired
    firmness. Once cooked, drain, rinse, and set aside.
\item Heat a skillet over medium heat with some oil. Then add prosciutto and cook until crispy (roughly 1 minute per add
    oil, side). Once cooked, remove and put it on a plate and set aside.
\item Return skillet to medium heat with some more oil. Once hot, add the contents of the onion/garlic/mushroom bowl.
    Cook, stirring occasionally, until tender (6-7 minutes)
\item Preheat the broiler on high.
\item Combine eggs, salt, pepper, and half of the Parmesan cheese in a bowl. Whisk together.
\item Crumble up the prosciutto in the egg bowl and whisk again.
\item At this point, the mushrooms and onions and spinach should be tender. Add the basil and spinach to the skillet in
    handfuls, waiting for the spinach to wilt slightly before adding the next handful.
\item Add the cooked pasta, drizzle with some additional olive oil, and toss to combine with the veggies.  Smooth them out into an even layer.
\item Pour the egg mixture over the pasta, making sure the prosciutto is evenly distributed over the top.  As the eggs
    set around the edge of the skillet, gently lift the cooked portions with a spatula to allow uncooked egg to flow
    underneath. Cook until bottom and sides are firm but the top is still runny (6-8 minutes).
\item Top the pan with the rest of the Parmesan and place under the broiler. Cook until golden brown (2-3 minutes).
\item Remove from oven, slice, serve, and eat well :)
\end{enumerate}
