\section{White Chicken Chili}

\begin{itemize}
\item 4 garlic cloves, minced
\item 1 large green bell pepper, seeded and chopped
\item 2 jalape\~{n}os, chopped (remove seeds to reduce spice)
\item 3 ribs celery, chopped
\item 1 medium yellow onion, chopped
\item 2 tsps ground cumin
\item 2 tsps dried oregano
\item 1 tsp ground coriander
\item 0.25 tsp cayenne pepper (optional)
\item 2 tsps salt
\item 2 cans cannellini beans, rinsed and drained
\item 1.5 lbs boneless skinless chicken thighs
\item 1 cup chicken broth
\item 1 cup sour cream
\item 0.5 cup chopped fresh cilantro
\end{itemize}

\begin{enumerate}
\item Select the saut\'e setting on the pressure cooker and heat olive oil and garlic for about 2 minutes until the
    garlic is bubbling.
\item Add the following and saut\'e for about 5 minutes, until the vegetables are softened.
\begin{itemize}
    \item bell pepper
    \item jalape\~{n}os
    \item celery
    \item onion
\end{itemize}
\item Add the following and saut\'e for another minute, or until aromatic.
\begin{itemize}
    \item cumin
    \item oregano
    \item coriander
    \item cayenne
    \item salt
\end{itemize}
\item Pour the beans over the vegetables, layer the chicken pieces on top, and pour in the broth. Do not stir!
\item Put the lid on the pressure cooker, cancel the saut\'e, and set to pressure cook on high for 15 minutes.
\item Let some of the pressure naturally release for a little bit before doing the quick release! Wait about 10 minutes.
\item Remove the chicken from the pressure cooker and shred it with two forks, then add it back to the pressure cooker
    with sour cream and cilantro.
\item Taste for seasoning!
\end{enumerate}
